Ceph Parallel File System Evaluation Report

### 2013-11-06 baseline.tex
fixing based on various review comments
more fixes based on the reviewer's comment

\section{Establishing A Performance Baseline}
\label{sec:baseline}

@@

The lowest layer in the system are the exposed LUNs to the server hosts from
the RAID controllers.  These LUNs are configured as a RAID 6 8+2 array (8 data
disks and 2 \textit{P} and \textit{Q} disks). In prior tests we observed
that a 7.2K RPM SAS disk can perform at \textasciitilde140 MB/s for 128 kB
sequential I/O requests and a 7.2K RPM SATA disk can do \textasciitilde36 MB/s.
For these tests, all disk caches were turned off. Therefore, in 8 data disk
RAID group with 1 MB sequential I/O requests (each disks sees 128 kB chunks of
the request) the expected aggregate performance would be \textasciitilde1.12
GB/s for a SAS RAID group and \textasciitilde288 MB/s for a SATA RAID group, if
there are no caches along the I/O path.  With the caches turned on, especially
the write-back cache on the DDN RAID controller, we observe a significant
performance improvement. In our day-to-day HPC operations we run our storage
systems with write-back cache turned on on RAID controllers, if and only if,
there is a method of cache-mirroring between the two active-active RAID
controllers. With the write-back cache on we observe \textasciitilde1.4 GB/s
per RAID 6 8+2 SAS group and  \textasciitilde955 MB/s per RAID 6 8+2 SATA
group, for 1 MB sequential I/O.  These two performance numbers will be used as
a baseline in our study and they are presented in
Table~\ref{tbl:block-io-baseline}.  For these tests, the 8+2 RAID 6 groups are
exported to the server hosts using SCSI RDMA Protocol (SRP) over IB protocol
(which is the default for our normal HPC configurations). For a SATA disk group
this translates into roughly 120 MB/s/disk and for a SAS disk group it is 175
MB/s/disk. As can be seen, SATA RAID groups benefit from caching more than SAS
groups.

>>>>

\section{Establishing A \\Performance Baseline}
\label{sec:baseline}

@@

The lowest layer in the system are the exposed LUNs to the server hosts from
the RAID controllers.  These LUNs are configured as a RAID 6 8+2 array (8 data
disks and 2 \textit{P} and \textit{Q} disks). In prior tests we observed
that a 7.2K RPM SAS disk can perform at 140 MB/s for 128 kB
sequential I/O requests and a 7.2K RPM SATA disk can do 36 MB/s.
For these tests, all disk caches were turned off. Therefore, in 8 data disk
RAID group with 1 MB sequential I/O requests (each disks sees 128 kB chunks of
the request) the aggregate performance is about 1.12
GB/s for a SAS RAID group and 288 MB/s for a SATA RAID group, if
there are no caches along the I/O path.  With the caches turned on, especially
the write-back cache on the DDN RAID controller, we observe a significant
performance improvement. In our day-to-day HPC operations we run our storage
systems with write-back cache turned on on RAID controllers, if and only if,
there is a method of cache-mirroring between the two active-active RAID
controllers. With the write-back cache on we observe \textasciitilde1.4 GB/s
per RAID 6 8+2 SAS group and  \textasciitilde955 MB/s per RAID 6 8+2 SATA
group, for 1 MB sequential I/O.  These two performance numbers will be used as
a baseline in our study and they are presented in
Table~\ref{tbl:block-io-baseline}.  For these tests, the 8+2 RAID 6 groups are
exported to the server hosts using SCSI RDMA Protocol (SRP) over IB protocol
(which is the default for our normal HPC configurations). For a SATA disk group
this translates into roughly 120 MB/s/disk and for a SAS disk group it is 175
MB/s/disk. As can be seen, SATA RAID groups benefit from caching more than SAS
groups.
